Optimized Synthesized Spectrum

### 2016-10-02 2016.10.3 Jason_v2.tex
Update 2016.10.3 Jason_v2.tex

Then fit \(y_{j,n}^{optimized} \) with \(y_{jn}\), where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. The optimization method we use is Levenberg - Marquardt algorithm.
a+b+c should be equal to 1.

@@

The result is \(a+b+c = 0.983661295269\). (a,b,c) = (0.338, 0.110, 0.536)

@@

 Then compare the chi-square for aspcapStar-v304-2M16421116+3618225 of the two methods:
 chi-square for \( y_{j,n}^{inferred}\) and \( y_{j,n}^{optimized}\) are 145.84 and 145.89
 They are similar to each other.

>>>>

Then fit \(y_{j,n}^{optimized} \) with \(y_{jn}\), where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. The optimization method we use is Levenberg - Marquardt algorithm.
a+b+c should be equal to 1.
\bigskip

There are some tricks in the fitting. Because the fitting module is very sensitive to the outliers in the spectrum data, we add a constant to the flux and subtract it after the fitting. The result is better because a+b+c is closer to 1, which is 0.996 compared to 0.983.
\bigskip
Also, we add a bound to the parameters to make b is bigger than a or c. set the range of b as (0.8,1.2)

@@

The result is \(a+b+c = 0.997\). (a,b,c) = (-0.005,0.810, 0.192)

@@

 Then compare the chi-square for aspcapStar-v304-2M16421116+3618225 of the two methods:
 chi-square for \( y_{j,n}^{inferred}\) and \( y_{j,n}^{optimized}\) are 302.41 and 304.21
 They are similar to each other.
